Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2025-01-11 manuscript/manuscript.qmd
Switch to {tinytable}

```{r libraries-data}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(ggforce)
library(ggh4x)
library(scales)
library(glue)
library(gt)
library(gtExtras)
library(modelsummary)
library(here)

@@

theme_set(theme_ngo())

gt_linebreak <- function(x) {
  if (fmt_out == "latex") {
    x %>% 
      str_replace_all("\\[", "{[}") %>% 
      str_replace_all("\\]", "{]}") %>% 
      kableExtra::linebreak(align = "c")
  } else {
    str_replace_all(x, "\\n", "<br>")
  }
}

fmt_markdown_latex <- function(x, columns) {
  if (fmt_out == "latex") {
    fmt_passthrough(x, columns = columns, escape = FALSE)
  } else {
    fmt_markdown(x, columns = columns)
  }
}

gt_pct <- function(x, page_width = 6) {
  if (fmt_out == "latex") {
    paste0(page_width * (x / 100), "in")
  } else {
    gt::pct(x)
  }
}
```

@@

\begingroup

::: {.content-visible when-profile="ms"}
\singlespacing
:::

::: {#tbl-design}

\footnotesize
\renewcommand*{\arraystretch}{1.75}

```{r}
#| label: table-design
#| include: true
transparency <- c("Doesn't engage in transparency", "Engages in transparency")
accountability <- c("Doesn't engage in accountability", "Engages in accountability")
govt <- c("Friendly relationship with government", "Criticized by government", "Under government crackdown")
orgs <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
funding <- c("Funded primarily by many small private donations", "Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")

@@

tbl_features_levels %>%
  rowwise() %>% 
  mutate(type = ifelse(
    fmt_out == "latex",
    str_replace_all(type, "~([^~]+)~", "\\\\textsubscript{\\1}"),
    type
  )) %>%
  gt() %>%
  cols_label(feature = "Feature/Attribute", levels = "Levels", type = "Purpose") %>%
  cols_width(feature ~ gt_pct(20), levels ~ gt_pct(50), type ~ gt_pct(15)) %>%
  fmt_markdown_latex(columns = c("type")) %>%
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>%
  opts_theme() |>
  tab_options(
    quarto.disable_processing = TRUE
  )
```

All experimental features and levels included in the conjoint experiment

:::

\endgroup

@@

After presenting respondents with a set of organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example). We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents). In order to estimate individual-specific differences using a multilevel model, each respondent had to complete multiple experimental tasks. Having choice of hypothetical organization indicate donation intention and asking respondents to iteratively make this choice across 12 experimental tasks are both typical of conjoint analysis.

::: {.content-visible when-profile="ms"}
\clearpage
:::

\begingroup

::: {.content-visible when-profile="ms"}
\singlespacing
:::

::: {#tbl-example}

\footnotesize
\renewcommand*{\arraystretch}{1.75}

```{r}
#| label: table-example
#| include: true
withr::with_seed(12345, {
  tbl_example_task <- tribble(
    ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
    "Organization", sample(orgs, 1), sample(orgs, 1), sample(orgs, 1), "—",
    "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
    "Transparency", sample(transparency, 1), sample(transparency, 1), sample(transparency, 1), "—",
    "Accountability", sample(accountability, 1), sample(accountability, 1), sample(accountability, 1), "—",
    "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",
    "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
  )
})

tbl_example_task %>%
  gt() %>%
  cols_align(align = "center", columns = everything()) %>%
  cols_align(align = "left", columns = Attribute) %>%
  cols_width(everything() ~ gt_pct(17)) %>%
  tab_style(
    style = cell_text(v_align = "top"),
    locations = cells_body()
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    location = cells_body(columns = Attribute)
  ) %>%
  opts_theme()
```

Example possible experimental task, with three randomized combinations of organizational attributes

:::

\endgroup

>>>>

```{r libraries-data}
library(tidyverse)
library(targets)
library(tidybayes)
library(patchwork)
library(ggforce)
library(ggh4x)
library(scales)
library(glue)
library(tinytable)
library(modelsummary)
library(here)

@@

theme_set(theme_ngo())
```

@@

```{r}
#| label: tbl-design
#| tbl-cap: "All experimental features and levels included in the conjoint experiment"
#| include: true
transparency <- c("Doesn't engage in transparency", "Engages in transparency")
accountability <- c("Doesn't engage in accountability", "Engages in accountability")
govt <- c("Friendly relationship with government", "Criticized by government", "Under government crackdown")
orgs <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
issues <- c("Emergency response", "Environment", "Human rights", "Refugee relief")
funding <- c("Funded primarily by many small private donations", "Funded primarily by a handful of wealthy private donors", "Funded primarily by government grants")

@@

tbl_features_levels %>%
  setNames(c("Type", "Feature/Attribute", "Levels")) %>%
  tt(width = c(0.15, 0.25, 0.5)) %>%
  style_tt(j = 1:3, align = "l") %>%
  format_tt(j = 1, markdown = TRUE) %>%
  style_tt(
    bootstrap_class = "table table-sm table-striped",
    tabularray_inner = "rowsep=2pt, cells={font=\\footnotesize}, row{1}={valign=b}"
  )
```

@@

After presenting respondents with a set of organizations, we asked them which of the three they would be willing to donate to, along with an option for no selection (see @tbl-example for an example). We then repeated the process eleven more times for a total of twelve randomized iterations of hypothetical combinations of attributes, resulting in 12,192 completed experimental tasks (12 iterations × 1,016 respondents). In order to estimate individual-specific differences using a multilevel model, each respondent had to complete multiple experimental tasks. Having the choice of hypothetical organization indicate donation intention and asking respondents to iteratively make this choice across twelve experimental tasks are both typical of conjoint analysis.

```{r}
#| label: tbl-example
#| tbl-cap: "Example possible experimental task, with three randomized combinations of organizational attributes"
#| include: true
withr::with_seed(12345, {
  tbl_example_task <- tribble(
    ~Attribute, ~`Option 1`, ~`Option 2`, ~`Option 3`, ~None,
    "Organization", sample(orgs, 1), sample(orgs, 1), sample(orgs, 1), "—",
    "Issue area", sample(issues, 1), sample(issues, 1), sample(issues, 1), "—",
    "Transparency", sample(transparency, 1), sample(transparency, 1), sample(transparency, 1), "—",
    "Accountability", sample(accountability, 1), sample(accountability, 1), sample(accountability, 1), "—",
    "Funding sources", sample(funding, 1), sample(funding, 1), sample(funding, 1), "—",
    "Relationship with host government", sample(govt, 1), sample(govt, 1), sample(govt, 1), "—"
  )
})

tbl_example_task %>%
  tt(width = rep(0.19, times = 5)) %>%
  style_tt(j = 1, align = "l", bold = TRUE) %>%
  style_tt(j = 2:5, align = "c") %>%
  style_tt(
    bootstrap_class = "table table-sm table-striped",
    tabularray_inner = "rowsep=2pt, cells={font=\\footnotesize}, row{1}={valign=b}"
  )
```
